How do changes in ex vary between countries?

### 2022-07-20 draft_working_paper.Rmd
add figure of average change

>>>>

ggsave("figures/proposed/average_improvement1980-2020.png", height = 20, width = 30, units = "cm", dpi = 300)

hmd_ex_selected_countries_with_synth %>% 
    filter(year >= 1979) %>% 
    filter(!(code %in% c("DEUTE", "DEUTW", "DEUTNP"))) %>%  # Using only synthetic germany for longer time period
    group_by(code, x, sex) %>% 
    arrange(year) %>% 
    mutate(delta_ex = ex - lag(ex)) %>% 
    nest() %>% 
    mutate(
      rwd_model = map(data, ~lm(delta_ex ~ 1, data = . )),
      ar_model  = map(data, ~lm(delta_ex ~ lag(delta_ex), data = .))
    ) %>% 
    mutate(
      aic_rwd = map_dbl(rwd_model, AIC),
      aic_ar  = map_dbl(ar_model, AIC)
    ) %>% 
    mutate(
      diff_aic = aic_ar - aic_rwd
    )  %>% 
  # filter(diff_aic > 0)
  mutate(
    tidied_ar_model = map(ar_model, broom::tidy)
  ) %>% 
  unnest(tidied_ar_model) %>% 
  filter(term == "(Intercept)") %>% 
  arrange(desc(estimate)) %>%
  left_join(country_code_lookup) %>% 
  mutate(country = factor(country, levels = c("England & Wales", "Scotland", "Synthetic Germany", "Spain", "France", "Italy", "Netherlands"))) %>%
  filter(!is.na(country)) %>% 
  select(code, country, x, sex, estimate, std.error) %>% 
  mutate(display_label = glue::glue("{country}_{x}_{sex}")) %>% 
  mutate(estimate_weeks = estimate * 52.25) %>% 
  ggplot(aes(estimate_weeks, fct_reorder(display_label, estimate_weeks))) + 
  geom_point(aes(colour = x), show.legend = FALSE) +
  expand_limits( x = 0) + 
  geom_vline(xintercept = 0) + 
  labs(
    x = "Average annual life expectancy change (weeks per year)",
    y = "Country-sex combination",
    title = "Average annual improvements by country and sex",
    subtitle = "Range: 1980 to 2020 or nearest available years",
    caption = "Source: Human Mortality Database"
  ) + 
  facet_wrap(~x)

ggsave("figures/proposed/reduced_average_improvement1980-2020.png", height = 20, width = 25, units = "cm", dpi = 300)
